State of the Practice for Medical Imaging Software

### 2021-12-14 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Added a bit more of an introduction to the RQs

To gain insights, we devised five research questions, which can be applied to
MI, as well as to other domains, of research software \citep{SmithEtAl2021}. The
first question below refers to artifacts.  We use this term to represent the
documents, scripts and code that constitutes a software development project.
Example artifacts include requirements, specifications, user manuals, unit
tests, system tests, usability tests, build scripts, API (Application
Programming Interface) documentation, READMEs, license documents, process
documents, and code.

>>>>

To gain insights, we devised five research questions, which can be applied to
MI, as well as to other domains, of research software \citep{SmithEtAl2021}. The
questions are designed to learn about the community's interest in, and
experience with, artifacts, tools, principles, processes, methodologies and
qualities.  When we mention artifacts we mean documents, scripts and code that
constitutes a software development project. Example artifacts include
requirements, specifications, user manuals, unit tests, system tests, usability
tests, build scripts, API (Application Programming Interface) documentation,
READMEs, license documents, process documents, and code.  We aimed to collect
enough information to understand the current pain points experienced by the MI
software development community so that we can make some preliminary
recommendations for future improvements.
